A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-01-25 manuscript.Rmd
switch to bookdown, so that figure references work

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: pdf_document
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: references.bib
---

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
output: bookdown::pdf_document2
repro:
  packages:
    - usethis
    - repro
    - here
csl: apa7.csl
bibliography: references.bib
---
